Simple Mediation Example

### 2017-06-12 mediation.Rmd
added note that I haven't updated the rest of the text in the document.
updated step by step to match function estimates.

```{r xy association}
# check mod estimates
# this is referered to the direct effect
te_mod <- tidy((glm(y~x, sim_data, family="binomial"(link="logit"))))
te_mod

@@

```{r xm and my association}
# linear x -> m mod beta
xm_mod <- tidy(glm(m~x, sim_data, family = "gaussian"(link="identity")))
xm_mod

# logit m -> y mod beta
my_mod <- tidy(glm(y~m, sim_data, family="binomial"(link="logit")))
my_mod

@@

```{r cde}
cde_mod <- tidy(glm(y~ x + m, sim_data, family="binomial"(link="logit")))  
cde_mod

@@

```{r mediation boot}
# booting 1000 times 
boot_mediation <- sim_data %>% bootstrap(1000) %>% 
  do(tidy(mediation(data=., y="y", x="x", m="m", c="c", y_family="poisson",
                 m_family="gaussian")))

@@

>>>>

```{r xy association}
# check mod estimates
# this is referered to the direct effect
te_mod <- tidy((glm(y~x+c, sim_data, family="poisson"(link = "log"))))
te_mod

@@

```{r xm and my association}
# linear x -> m mod beta
xm_mod <- tidy(glm(m~x+c, sim_data, family = "gaussian"(link="identity")))
xm_mod

# logit m -> y mod beta
my_mod <- tidy(glm(y~m+c, sim_data, family="poisson"(link="log")))
my_mod

@@

```{r cde}
cde_mod <- tidy(glm(y~ x + m + c, sim_data, family="poisson"(link="log")))  
cde_mod

@@

```{r mediation boot}
set.seed(321)
# booting 1000 times 
boot_mediation <- sim_data %>% bootstrap(1000) %>% 
  do(tidy(mediation(data=., y="y", x="x", m="m", c="c", y_family="poisson",
                 m_family="gaussian")))

@@

### TO DO

I haven't modified the rest of the document after updating the funciton to handle confounding.
